---
title: "xy_descriptive_association between variables"
author: "EF"
date: "3/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RCurl)
library(tidyverse)
library(lme4)
library(here)
```

# Descriptive statistical analysis

**Part2**
```{r echo=FALSE}
level1 <- read.csv(here("level1data.csv"))
level2 <- read.csv(here("level2data.csv"))
```


```{r echo=FALSE}
##create variables for analyses
#level1 data processing: compute a variable from existing columns
level1 <- level1 %>% 
  mutate(POS4.3 = rowMeans(level1[,c('po_interested','po_excited','po_proud')], na.rm=TRUE)) %>% 
  mutate(NEG4.3 = rowMeans(level1[,c('ne_sad','ne_ashamed','ne_irritable','ne_nervous',
                                     'ne_guilty','ne_scared','ne_afraid')], na.rm=TRUE)) %>% 
  mutate(POS5.2 = rowMeans(level1[,c('UnhappyEvent_interested','UnhappyEvent_excited','UnhappyEvent_proud')], na.rm=TRUE)) %>% 
  mutate(NEG5.2 = rowMeans(level1[,c('UnhappyEvent_sad','UnhappyEvent_ashamed','UnhappyEvent_irritable','UnhappyEvent_nervous',
                                 'UnhappyEvent_guilty','UnhappyEvent_scared','UnhappyEvent_afraid')], na.rm=TRUE)) %>% 
  mutate(POS6.2 = rowMeans(level1[,c('HappyEvent_interested','HappyEvent_excited','HappyEvent_proud')], na.rm=TRUE)) %>% 
  mutate(NEG6.2 = rowMeans(level1[,c('HappyEvent_sad','HappyEvent_ashamed','HappyEvent_irritable','HappyEvent_nervous',
                                 'HappyEvent_guilty','HappyEvent_scared','HappyEvent_afraid')], na.rm=TRUE)) %>% 
#recode a categorical variable into a new binary variable
  mutate(UnhappySocial = case_when(UnhappyEvent == 21 ~ 1L,
                                   UnhappyEvent == 22 ~ 1L,
                                   UnhappyEvent == 23 ~ 1L,
                                   UnhappyEvent == 11 ~ 0L,
                                   UnhappyEvent == 12 ~ 0L,
                                   UnhappyEvent == 13 ~ 0L,
                                   UnhappyEvent == 3 ~ 0L,
                                   UnhappyEvent == 4 ~ 0L)) %>% 
  mutate(device5 = case_when(UnhappyEventRegulation_phone == 11 ~ 1L,
                             UnhappyEventRegulation_phone == 12 ~ 0L,
                             UnhappyEventRegulation_phone == 21 ~ 0L)) %>% 
  mutate(HappySocial = case_when(HappyEvent == 21 ~ 1L,
                                   HappyEvent == 22 ~ 1L,
                                   HappyEvent == 23 ~ 1L,
                                   HappyEvent == 11 ~ 0L,
                                   HappyEvent == 12 ~ 0L,
                                   HappyEvent == 13 ~ 0L,
                                   HappyEvent == 3 ~ 0L,
                                   HappyEvent == 4 ~ 0L)) %>% 
  mutate(device6 = case_when(HappyEventRegulation_phone == 11 ~ 1L,
                             HappyEventRegulation_phone == 12 ~ 0L,
                             HappyEventRegulation_phone == 21 ~ 0L))


#Level2 data processing: compute a variable from existing columns
level2 <- level2 %>% 
  mutate(online = rowMeans(level2[,c('OnlineSocialSupport1','OnlineSocialSupport2','OnlineSocialSupport3','OnlineSocialSupport4',
                                 'OnlineSocialSupport5','OnlineSocialSupport6','OnlineSocialSupport7','OnlineSocialSupport8',
                                 'OnlineSocialSupport9','OnlineSocialSupport10','OnlineSocialSupport11')], na.rm=TRUE)) %>% 
  mutate(offline = rowMeans(level2[,c('OfflineSocialSupport1','OfflineSocialSupport2','OfflineSocialSupport3',
                                      'OfflineSocialSupport4','OfflineSocialSupport5','OfflineSocialSupport6',
                                      'OfflineSocialSupport7','OfflineSocialSupport8','OfflineSocialSupport9',
                                      'OfflineSocialSupport10','OfflineSocialSupport11')], na.rm=TRUE)) %>% 
  mutate(soAnxiety = rowMeans(level2[,c('SocialAnxiety1','SocialAnxiety2','SocialAnxiety3','SocialAnxiety4',
                                        'SocialAnxiety5','SocialAnxiety6','SocialAnxiety7','SocialAnxiety8',
                                        'SocialAnxiety9','SocialAnxiety10')], na.rm = TRUE)) %>% 
  mutate(soEfficacy = rowMeans(level2[,c('SocialSelfEfficacy1','SocialSelfEfficacy2','SocialSelfEfficacy3','SocialSelfEfficacy4',
                                        'SocialSelfEfficacy5','SocialSelfEfficacy6')], na.rm = TRUE)) %>% 
  mutate(addiction = rowMeans(level2[,c('Addiction1','Addiction2','Addiction3','Addiction4','Addiction5',
                                       'Addiction6','Addiction7','Addiction8','Addiction9','Addiction10')], na.rm = TRUE)) %>% 
  mutate(paInvolve = rowMeans(level2[,c('ParentalSchoolInvolvement1','ParentalSchoolInvolvement2','ParentalSchoolInvolvement3',
                                        'ParentalSchoolInvolvement4','ParentalSchoolInvolvement5','ParentalSchoolInvolvement6',
                                        'ParentalSchoolInvolvement7','ParentalSchoolInvolvement8','ParentalSchoolInvolvement9',
                                        'ParentalSchoolInvolvement10')], na.rm = TRUE)) %>% 
  mutate(selfControl = rowMeans(level2[,c('SelfControl1','SelfControl2','SelfControl3','SelfControl4','SelfControl5',
                                          'SelfControl6')], na.rm = TRUE)) %>% 
  mutate(emoEfficacy = rowMeans(level2[,c('EmotionRegulationEfficacy1','EmotionRegulationEfficacy2','EmotionRegulationEfficacy3',
                                          'EmotionRegulationEfficacy4','EmotionRegulationEfficacy5','EmotionRegulationEfficacy6',
                                          'EmotionRegulationEfficacy7','EmotionRegulationEfficacy8','EmotionRegulationEfficacy9',
                                          'EmotionRegulationEfficacy10','EmotionRegulationEfficacy11','EmotionRegulationEfficacy12')], na.rm = TRUE)) %>% 
  #recode a numeric variable to a new binary variable
  mutate(gender = recode(
    Gender,
    `1` = 0L, `2` = 1L
  ))

#recode nominal variables and center continuous variables
level1 <- level1 %>% 
  mutate(motive = recode(
    FirstMotivation,
    d = "subconscious", D = "subconscious", a = "bored", A = "bored", c = "emergency", C = "emergency",
    b = "learning", B = "learning", 
    e = "not in learning state", E = "not in learning state", 
    F = "bad mood", f = "bad mood")
  ) %>% 
  mutate(posbi = ifelse(POS4.3 <=1, 0L, 1L)) %>% 
  mutate(negbi = ifelse(NEG4.3 <=1, 0L, 1L)) %>% 
  mutate_if(is.list, as.factor)%>%
  mutate(motivef = factor(
    motive,
    levels = c("subconscious", "bad mood",  "bored", "emergency", "learning",  "not in learning state")
  ))



#join certain level1 and level2 variables.
df1 <-  level1 %>% 
  select(ID, posbi, negbi, motivef, HappySocial:device6)

df2 <- level2 %>% 
  select(ID, addiction, Age, gender, Hukou,Grade, AgeAtFirstPhoneUse, WeekdaysPhoneUse, WeekendPhoneUse)

df <- df1 %>% 
  select(-HappySocial, -device6) %>% 
  left_join(df2, by = "ID")

df <- df %>% 
  mutate(Caddiction = addiction - mean(addiction)) %>% 
  mutate(CAge = Age - mean(Age))
```

##Associations between two categorical variables
```{r echo=FALSE}
chisq.test(df$posbi,df$gender)
chisq.test(df$posbi,df$Hukou)
chisq.test(df$posbi,df$Grade)
chisq.test(df$negbi,df$gender)
chisq.test(df$negbi,df$Hukou)
chisq.test(df$negbi,df$Grade)
chisq.test(df$gender,df$Hukou)
chisq.test(df$gender,df$Grade)
chisq.test(df$Hukou,df$Grade)
```

##Associations between one categorical variable and one continous variable

###Association between Positive emotion and addiction
```{r echo=FALSE}
Posbi_1 <- 
  df %>% 
  filter(posbi == 1) %>% 
  select(addiction) %>% 
  pull()

Posbi_0 <- 
  df %>% 
  filter(posbi == 0) %>% 
  select(addiction) %>% 
  pull()

fit1 <- t.test(Posbi_1, Posbi_0)
fit1
```

###Association between Positive emotion and Age
```{r echo=FALSE}
Posbi_1 <- 
  df %>% 
  filter(posbi == 1) %>% 
  select(Age) %>% 
  pull()

Posbi_0 <- 
  df %>% 
  filter(posbi == 0) %>% 
  select(Age) %>% 
  pull()

fit1 <- t.test(Posbi_1, Posbi_0)
fit1
```

###Association between positive emotion and AgeAtFirstPhoneUse
```{r echo=FALSE}
Posbi_1 <- 
  df %>% 
  filter(posbi == 1) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()

Posbi_0 <- 
  df %>% 
  filter(posbi == 0) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()

fit1 <- t.test(Posbi_1, Posbi_0)
fit1
```

###Association between positive emotion and the number hours that the participant used phone during weekdays
```{r echo=FALSE}
Posbi_1 <- 
  df %>% 
  filter(posbi == 1) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()

Posbi_0 <- 
  df %>% 
  filter(posbi == 0) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()

fit1 <- t.test(Posbi_1, Posbi_0)
fit1
```

###Association between positive emotion and the number of hours that the participant used phone during weekends
```{r echo=FALSE}
Posbi_1 <- 
  df %>% 
  filter(posbi == 1) %>% 
  select(WeekendPhoneUse) %>% 
  pull()

Posbi_0 <- 
  df %>% 
  filter(posbi == 0) %>% 
  select(WeekendPhoneUse) %>% 
  pull()

fit1 <- t.test(Posbi_1, Posbi_0)
fit1
```

###Association between negative emotion and participant's score on addictive smartphone use
```{r echo=FALSE}
Negbi_1 <- 
  df %>% 
  filter(negbi == 1) %>% 
  select(addiction) %>% 
  pull()

Negbi_0 <- 
  df %>% 
  filter(negbi == 0) %>% 
  select(addiction) %>% 
  pull()

fit1 <- t.test(Negbi_1, Negbi_0)
fit1
```

###Association between negative emotion and participant's age
```{r echo=FALSE}
Negbi_1 <- 
  df %>% 
  filter(negbi == 1) %>% 
  select(Age) %>% 
  pull()

Negbi_0 <- 
  df %>% 
  filter(negbi == 0) %>% 
  select(Age) %>% 
  pull()

fit1 <- t.test(Negbi_1, Negbi_0)
fit1
```

###Association between negative emotion and AgeAtFirstPhoneUse
```{r echo=FALSE}
Negbi_1 <- 
  df %>% 
  filter(negbi == 1) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()

Negbi_0 <- 
  df %>% 
  filter(negbi == 0) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()

fit1 <- t.test(Negbi_1, Negbi_0)
fit1
```

###Association between negative emotion and the number of hours participant used phone on weekdays
```{r echo=FALSE}
Negbi_1 <- 
  df %>% 
  filter(negbi == 1) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()

Negbi_0 <- 
  df %>% 
  filter(negbi == 0) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()

fit1 <- t.test(Negbi_1, Negbi_0)
fit1
```

###Association between negative emotion and number of hours participant used phone on a weekend day
```{r echo=FALSE}
Negbi_1 <- 
  df %>% 
  filter(negbi == 1) %>% 
  select(WeekendPhoneUse) %>% 
  pull()

Negbi_0 <- 
  df %>% 
  filter(negbi == 0) %>% 
  select(WeekendPhoneUse) %>% 
  pull()

fit1 <- t.test(Negbi_1, Negbi_0)
fit1
```

### Association between gender and participant's score on addictive smartphone use
```{r echo=FALSE}
Gender_1 <- 
  df %>% 
  filter(gender == 1) %>% 
  select(addiction) %>% 
  pull()

Gender_0 <- 
  df %>% 
  filter(gender == 0) %>% 
  select(addiction) %>% 
  pull()

fit1 <- t.test(Gender_1, Gender_0)
fit1
```

###Association between gender and the participant's age
```{r echo=FALSE}
Gender_1 <- 
  df %>% 
  filter(gender == 1) %>% 
  select(Age) %>% 
  pull()

Gender_0 <- 
  df %>% 
  filter(gender == 0) %>% 
  select(Age) %>% 
  pull()

fit1 <- t.test(Gender_1, Gender_0)
fit1
```

###Association between gender and AgeAtFirstPhoneUse
```{r echo=FALSE}
Gender_1 <- 
  df %>% 
  filter(gender == 1) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()

Gender_0 <- 
  df %>% 
  filter(gender == 0) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()

fit1 <- t.test(Gender_1, Gender_0)
fit1
```

###Association between gender and the number of hours participant used phone on a weekday
```{r echo=FALSE}
Gender_1 <- 
  df %>% 
  filter(gender == 1) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()

Gender_0 <- 
  df %>% 
  filter(gender == 0) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()

fit1 <- t.test(Gender_1, Gender_0)
fit1
```

###Association between gender and the number of hours participant used phone on a weekend day
```{r echo=FALSE}
Gender_1 <- 
  df %>% 
  filter(gender == 1) %>% 
  select(WeekendPhoneUse) %>% 
  pull()

Gender_0 <- 
  df %>% 
  filter(gender == 0) %>% 
  select(WeekendPhoneUse) %>% 
  pull()

fit1 <- t.test(Gender_1, Gender_0)
fit1
```

### Association between Hukou and Age
```{r echo=FALSE}
HukouAge <- aov(Age ~ Hukou, data = df)
summary(HukouAge)
```

###Association between Hukou and AgeAtFirstPhoneUse
```{r echo=FALSE}
HukouAgeAtFirstPhoneUse <- aov(AgeAtFirstPhoneUse ~ Hukou, data = df)
summary(HukouAgeAtFirstPhoneUse)
```

###Association between Hukou and addictive smartphone use
```{r echo=FALSE}
Hukouaddiction <- aov(addiction ~ Hukou, data = df)
summary(Hukouaddiction)
```

###Association between Hukou and the number of hours participant used phone on a weekday
```{r echo=FALSE}
HukouWeekdaysPhoneUse <- aov(WeekdaysPhoneUse ~ Hukou, data = df)
summary(HukouWeekdaysPhoneUse)
```

###Association between Hukou and the number of hours the participant used phone on a weekend day
```{r echo=FALSE}
HukouWeekendPhoneUse <- aov(WeekendPhoneUse ~ Hukou, data = df)
summary(HukouWeekendPhoneUse)
```

### Association between Grade and Age
```{r echo=FALSE}
Grade_7 <- 
  df %>% 
  filter(Grade == 1) %>% 
  select(Age) %>% 
  pull()

Grade_8 <- 
  df %>% 
  filter(Grade == 2) %>% 
  select(Age) %>% 
  pull()
fit1 <- t.test(Grade_7, Grade_8)
fit1
```

###Association between grade and AgeAtFirstPhoneUse
```{r echo=FALSE}
Grade_7 <- 
  df %>% 
  filter(Grade == 1) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()

Grade_8 <- 
  df %>% 
  filter(Grade == 2) %>% 
  select(AgeAtFirstPhoneUse) %>% 
  pull()
fit1 <- t.test(Grade_7, Grade_8)
fit1
```

###Association between Grade and addictive smartphone use
```{r echo=FALSE}
Grade_7 <- 
  df %>% 
  filter(Grade == 1) %>% 
  select(addiction) %>% 
  pull()

Grade_8 <- 
  df %>% 
  filter(Grade == 2) %>% 
  select(addiction) %>% 
  pull()
fit1 <- t.test(Grade_7, Grade_8)
fit1
```

###Association between Grade and number of hours the participant used phone on a weekday
```{r echo=FALSE}
Grade_7 <- 
  df %>% 
  filter(Grade == 1) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()

Grade_8 <- 
  df %>% 
  filter(Grade == 2) %>% 
  select(WeekdaysPhoneUse) %>% 
  pull()
fit1 <- t.test(Grade_7, Grade_8)
fit1
```

###Association between Grade and the number of hours participant used phone on weekend days
```{r echo=FALSE}
Grade_7 <- 
  df %>% 
  filter(Grade == 1) %>% 
  select(WeekendPhoneUse) %>% 
  pull()

Grade_8 <- 
  df %>% 
  filter(Grade == 2) %>% 
  select(WeekendPhoneUse) %>% 
  pull()
fit1 <- t.test(Grade_7, Grade_8)
fit1
```

## Association between two continuous variables
```{r echo=FALSE}
addiction_Age <- cor.test(df$addiction, df$Age, method = "pearson")
addiction_Age

addiction_AgeAtFirstPhoneUse <- cor.test(df$addiction, df$AgeAtFirstPhoneUse, method = "pearson")
addiction_AgeAtFirstPhoneUse

addiction_WeekdaysPhoneUse <- cor.test(df$addiction, df$WeekdaysPhoneUse, method = "pearson")
addiction_WeekdaysPhoneUse

addiction_WeekendPhoneUse <- cor.test(df$addiction, df$WeekendPhoneUse, method = "pearson")
addiction_WeekendPhoneUse

AgeAtFirstPhoneUse_Age <- cor.test(df$AgeAtFirstPhoneUse, df$Age, method = "pearson")
AgeAtFirstPhoneUse_Age

WeekdaysPhoneUse_Age <- cor.test(df$WeekdaysPhoneUse, df$Age, method = "pearson")
WeekdaysPhoneUse_Age

WeekendPhoneUse_Age <- cor.test(df$WeekendPhoneUse, df$Age, method = "pearson")
WeekendPhoneUse_Age

WeekdaysPhoneUse_AgeAtFirstPhoneUse <- cor.test(df$WeekdaysPhoneUse, df$AgeAtFirstPhoneUse, method = "pearson")
WeekdaysPhoneUse_AgeAtFirstPhoneUse

WeekendPhoneUse_Age <- cor.test(df$WeekendPhoneUse, df$AgeAtFirstPhoneUse, method = "pearson")
WeekendPhoneUse_Age

WeekdaysPhoneUse_WeekendPhoneUse <- cor.test(df$WeekdaysPhoneUse, df$WeekendPhoneUse, method = "pearson")
WeekdaysPhoneUse_WeekendPhoneUse
```

